Improvement of Deterministic NVT Molecular Dynamics via Backward Error Analysis

### 2018-06-06 rigid_bodies_supp_info.tex
results

\begin{table}
	\caption{Effect of the time-step size on .... of 903 TIP3P\cite{Jorgensen_1983} water molecules in NVT MD simulations employing the unsplit solution for free rotations, given by the numerical schemes.}
    \label{table:stability_martyna}
    \begin{tabular}{SS[table-number-alignment = center,table-figures-exponent = 1]S[table-number-alignment = center,table-figures-exponent = 1]}
     & \multicolumn{2}{c}{Martyna \textit{et al.} \cite{Martyna_1996}}  \\
     \cmidrule[0.5mm](lr){2-3} 
     $\timestep$ $\text{(fs)}$  & $\modified{H}$  & $\modified{\Ham{}}$     \\
	1 &  -1.6e-2  & 4.5e-3\\
	2 & 9.5e-2 & 1.4e-1\\
	3 & 2.8e-1 & 5.6e-2\\
	4 & 1.1e0 & 5.6e-2\\
	5 & 3.3e0 & -3.7e-2\\
    6 & 6.1e1 & 6.9e-2 \\
	7 & 9.8e2 & -3.6e-3 \\
	8 & 1.1e4 & 1.8e-2 \\
	9 & 7.5e4 & 3.8e-3 \\
	10 & 3.3e5 & 1.9e-2  \\
	\end{tabular}
\end{table}

>>>>

\begin{table}
	\caption{Effect of the time-step size on .... of 903 TIP3P\cite{Jorgensen_1983} water molecules in NVT MD simulations employing the unsplit solution for free rotations, given by the numerical schemes.}
    \label{table:stability}
        \sisetup{table-number-alignment = center}
    \begin{tabular}{SS[table-figures-decimal=1,table-figures-exponent = 1]S[table-figures-exponent = 1,table-figures-decimal=1]S[table-figures-decimal=1,table-figures-exponent = 1]S[table-figures-exponent = 1,table-figures-decimal=1]S[table-figures-exponent = 1,table-figures-decimal=1]}
     & \multicolumn{5}{c}{Drift rate [(kcal/mol)/ns]}  \\
     & \multicolumn{2}{c}{This work} & \multicolumn{2}{c}{Martyna \textit{et al.} \cite{Martyna_1996}}   & \multicolumn{1}{c}{NVE \cite{Silveira_2017}} \\
     \cmidrule[0.5mm](lr){2-3} \cmidrule[0.5mm](lr){4-5} \cmidrule[0.5mm](lr){6-6}  
     $\timestep$ $\; \text{(fs)}$  & $\modified{H}$  & $\modified{\Ham{}}$  & $H$  & $\modified{\Ham{}}$     & $\modified{\Ham{}}$   \\
	1 &  4.6e-4  & 8.5e-2 & -1.6e-2  & 4.5e-3 & -1.e-3 \\
	2 & -8.2e-3 & -4.3e-2 &  9.5e-2 & 1.4e-1 &  9.3e-3 \\
	3 & -3.2e-2 & 7.3e-2 & 2.8e-1 & 5.6e-2 & -5.0e-3 \\
	4 & 8.1e-3 & -1.1e-1 & 1.1e0 & 5.6e-2 & 8.5e-2 \\
	5 & 1.3e0 & -2.2e-2 & 3.3e0 & -3.7e-2 & 1.1e0 \\
    6 & 4.4e1 & -3.4e-3 & 6.1e1 & 6.9e-2 & 6.0e1 \\
	7 & 8.8e2 & 2.2e-2  & 9.8e2 & -3.6e-3 & \text{-} \\
	8 & 9.8e3 & 7.6e-2  & 1.1e4 & 1.8e-2 & \text{-} \\
	9 & 7.1e4 & -2.5e-2  & 7.5e4 & 3.8e-3 & \text{-} \\
	10 & 3.2e5 & -3.2e-2  & 3.3e5 & 1.9e-2  & \text{-} \\
	\end{tabular}
\end{table}

ADD: COMPARE MILLER WITH AND WITHOUT RESPA
ADD: CORRELATION FUNCTION AS A FUNCTION OF MASS PARAMETER OF THERMOSTAT

\begin{table*}
	\caption{Effect of the time-step size on .... of 903 TIP3P\cite{Jorgensen_1983} water molecules in NVT MD simulations employing the unsplit solution for free rotations, given by the numerical schemes....}
	\label{table:check_ens}
	\sisetup{table-number-alignment = center}
    \begin{tabular}{SS[separate-uncertainty,table-figures-uncertainty = 2]SS[separate-uncertainty,table-figures-uncertainty= 1]SS[separate-uncertainty,table-figures-uncertainty= 1]S}
	{$\timestep$} & {estimated $\Delta T$} & {$\sigma$ deviations}  & {estimated $\Delta T$}  & {$\sigma$ deviations}  &    {estimated $\Delta T$}  & {$\sigma$ deviations} \\
	{(fs)} & {(K)} &   & {(K)}  &  & {(K)}  & \\
			\hline
			\multicolumn{7}{c}{This work (Unsplit)}\\
1.0	& 3.02(2) & 1.07 & & & &  \\
2.0 & 3.02(2) & 0.81 & & & &  \\
3.0 & 2.98(2) & 0.73 & & & &  \\
4.0 & 3.01(2) & 0.41 & & & &  \\
5.0 & 3.02(2) & 0.79 & & & &  \\
6.0 & 3.03(3) & 1.23 & & & &  \\
7.0 & 2.98(2) & 0.74 & & & &  \\
            \hline
			\multicolumn{7}{c}{Martyna \textit{et al.} \cite{Martyna_1996}}\\
1.0	& 2.98(2) & 0.66 & 3.01(2) & 0.49 & 2.96(3) & 0.90 \\
2.0 & 2.98(2) & 0.73 & 2.99(2) & 0.03 & 3.02(3) & 0.66 \\
3.0 & 2.95(2) & 2.33 & 3.01(2) & 0.65 & 2.91(3) & 2.47 \\
4.0 & 3.00(2) & 0.01 & 3.01(2) & 0.72 & 2.92(3) & 2.19  \\
5.0 & 2.93(2) & 3.05 & 3.01(2) & 0.70 & 2.94(3) & 1.58  \\
6.0 & 2.92(2) & 3.87 & 3.00(2) & 0.22 & 2.91(3) & 2.76  \\
7.0 & 2.89(2) & 5.35 & 3.02(1) & 1.33 & 2.87(2) & 4.33  \\
            \hline
			\multicolumn{7}{c}{Kamberaj \textit{et al.} \cite{Kamberaj_2005}}\\
1.0	& 2.97(2) & 1.16 & 2.99(2) & 0.16 & 2.89(3) & 2.84  \\
2.0 & 3.00(2) & 0.02 & 3.02(2) & 0.99 & 2.00(4) & 0.25  \\
3.0 & 2.99(4) & 0.18 & 3.08(4) & 4.09 & 3.1(1) & 1.17  \\
4.0 & 2.92(8) & 0.99 & 3.12(2) & 6.01 & 2.8(2) & 0.95  \\
5.0 & 3.02(5) & 0.40 & 3.2(2)  & 9.50 &  2.9(1) & 0.28  \\
6.0 & 3.14(5) & 2.69 & 3.29(2) & 14.68 & 3.21(7) & 2.90  \\
7.0 & 3.03(4) & 0.73 & 3.35(2) & 17.37 & 2.99(6) & 0.16  \\
    \end{tabular}
\end{table*}
